% This file is not a standalone latex file; it is meant to be included within a
% master file.  You've been warned!

\chapter{The Death of Brian}

Brian considered his current situation.  He was currently laying on his back;
not unusual given the amount of alcohol he'd consumed.  There was a large man in
a toga jumping up and down on his chest while screaming at him; again, not an
unusual occurrence for him.  Yet, something didn't feel right about what was
going on.  It took him a few moments to realize what was strange about the
situation; first, his cousin Jared wasn't there either demanding payment for a
lost bet, or bemoaning payment for a bet Brian had won, and second, instead of
cursing Brian for whatever transgressions he had done, the man in the toga kept
screaming ``What time is it??? What is the date?!?''. When Brian didn't answer
immediately, the man proceeded bounce Brian's head against the ground like a
basketball.  While this didn't cause Brian the least bit of pain (`must be the
alcohol' mused Brian), it did make it hard to see his surroundings.

``Uhhhh... November 12, 2013?  Maybe around 3?'' 

``Morning or afternoon?!? \emph{MORNING OR AFTERNOON?!?!?!}'' screamed the man
with far more exclamation points than was strictly necessary.

``I'm... not sure..'' As a strong believer in the old saying `it's 5 o'clock
somewhere', it was difficult for Brian to determine a more accurate time solely
from the fact that he was drunk; although, he realized, he was in fact strangely
completely sober.

The man in the toga gave Brian a dirty look, jumped off of him and immediately
started screaming ``2013 November 12, 2100 hours plus/minus 6 hours, probability
0.2!!!''  This cry was picked up by several other people in the immediate area,
all of which started running in opposite directions.  Brian got up and noticed a
small squad of people furiously working on what appeared to be:
\begin{itemize}
    \item A holographic computer
    \item An abacus
    \item A complicated set of strings with knots in them
    \item A calculator
    \item Mud
    \item Fingers (and in one case, toes)
\end{itemize}
As they got their results, they each excitedly shouted different answers; Brian
caught the answers ``2017 AD December 21, 1634.65 plus/minus 224 seconds,
probability 0.55, \emph{MARK}!'' and ``34,351,657 BC May 3, 0352.3 plus/minus
12 seconds, probability 0.23, \emph{MARK}!'', but the rest of the answers seemed
to be in utterly alien languages.  Brian quietly escaped; no-one took any notice
of him.

`OK, there has got to be a reasonable explanation for all this,' thought Brian
to himself.  `I must have won the bet, and Jared must have gotten pissed and
committed me to the nut house as revenge.' He thought more about this and
realized that it fit all the evidence completely. When the guy in the toga was
bouncing his head on the ground, it must not have hurt because he was in a
padded room.  He must have been drugged heavily, so he not only was passed the
drunk stage, he was so far past hungover that he was clean sober.  And all the
screaming people yelling about the time clearly had some kind of weird time
fetish.  So all he really had to do was figure out how Jared had gotten him
committed in the first place, get out, and then get Jared committed as revenge.

`The trick is figuring out how to get out of here.  Maybe I can convince
everyone that I \emph{am} Jared, escape, and let them pick him up instead; he'll
\emph{never} see that one coming!'

Feeling far better about his prospects, Brian did what he did third
best\footnote{Drinking far more alcohol than anyone sane person would believe
possible was what he did best.  Running while drunk was what he did second
best.}; walk about at random until something interesting happened, or someone
started shouting ``that's him officer, quick arrest him!''\footnote{Which is why
the thing he did second best was run while drunk; he had lots of practice.}

After a time that seemed both interminable and utterly fleeting, Brian realized
that someone was watching him.
